Mitigating object prior-bias from sparse-projection tomographic reconstructions

### 2022-02-16 paper/response_2022.tex

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage[colorlinks=true]{hyperref}
\title{Author Response to Reviewers for the paper `Mitigating object
  prior-bias in sparse projection tomographic reconstructions'} 
\begin{document}
\date{}
\maketitle

@@

  \textbf{Response:} We had earlier shared code for 2D reconstructions
  \href{https://github.com/preetigopal/Weighted-Prior-Tomographic-Reconstruction}{in
    our github repository}. To this, we have now added code for 3D
  reconstructions for all datasets.

  \vspace{0.5cm}\textcolor{blue}{\textbf{[R1-4]:} \textit{In page 7 and lines 39-42
      left column, what are the weights for? I don't see any equation
      where these can be substituted for quantifying results. Also,
      RMSE and \hypertarget{ssim-R1}{SSIM have their own definitions}.}}

  \textbf{Response:} This point has come up in R2 as well (in a larger
  context), and we defer our detailed response to that section \textcolor{blue}{\textbf{\hyperlink{ssim}{[R2-1]}}}. In
  general, we agree that our earlier usage of the term `weights' with
  respect to SSIM might have been confusing since we also refer to
  `weights-map' throughout our paper.

  \vspace{0.5cm}\textcolor{blue}{\textbf{\hypertarget{hyperparameters}{[R1-5, 6]:}} \textit{In
      page 7 and lines 52-56 left column, I don't understand your
      tuning of $\lambda_1$. How is SSIM optimized when ground-truth
      is unknown for the test volume?  It appears that the weight
      $\lambda_2$ must be chosen carefully and sufficiently high to
      ensure that we achieve the very fidelity reconstruction shown in
      Fig. 11 (h) with just 6 views. A lower incorrect choice for
      $\lambda_2$ will certainly bring back the artifacts. Even the
      parameter k probably plays an important role in achieving
      Fig. 11(h). Thus, your explanation for choosing $\lambda_2$ (in
      page 7 and lines 8-10 right column) and k (in page 7 and lines
      23-27 right column) is inadequate. If you base your choice of
      $\lambda_2$ and k on "tolerance for noise" and/or "artifacts",
      how do you even quantify the relevant noise and artifacts? If
      $\lambda_2$ and k are chosen incorrectly, I am sure your method
      won't work. Hence, this detail needs to be discussed.}}

@@

\item \emph{ \ldots all steps \ldots} We also provide the details
  required.  We note that the TV reconstruction \emph{is} our pilot
  reconstruction and hence the computation times are equal.

  Having specified the exact compute times in our machine, we also
  note that the type of machine and the degree of parallelism
  available in the current times make these timing measurements,
  especially for iterative solutions, subjective.

\end{enumerate}

\begin{figure}[p]
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_1.png}
\captionsetup{labelformat=empty}       
% \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_2.png}
\captionsetup{labelformat=empty}
%        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_3.png}
\captionsetup{labelformat=empty}
%        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.19\linewidth}
        \includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/templateCropped_4.png}
\captionsetup{labelformat=empty}
%        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.186\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth, height=0.2\textheight]{../images/thesis/okra/testCropped.png}}
\captionsetup{labelformat=empty}
%        \caption{}
     \end{subfigure}
     \caption[Okra 3D dataset]{One slice each from the templates and
       one from the test volume (extreme right). In the regions marked
       in red and green, while all slices have deformities, the test
       has none.}
\label{fig:templates_test_okra}
%\end{figure}
%\begin{figure}[p]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/testCropped.png}}\hfill
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/fdk_cropped.png}}\hfill
%\subcaptionbox{CS,no prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/cs_cropped.png}}\hfill
\subcaptionbox{Unweighted \\prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/pca_cropped.png}}\hfill
\subcaptionbox{Weighted prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/prior_weighted_cropped.png}}
\caption[3D reconstruction of okra dataset]{Reconstruction from $10\%$
  views: (b) strong streak artefacts, %(c) blurred,
  (c) no new
  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (d) new information detected (no deformities
  corresponding to red and green regions) while simultaneously
  reducing streak artefacts.}
\label{fig:okra_3D_results}
%\end{figure}
%\begin{figure}[p]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/input_cropped.png}}\hfill
\subcaptionbox{FDK}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/FDK_cropped.png}}\hfill
%\subcaptionbox{Sparsity prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Unweighted \\prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/pca_cropped.png}}\hfill
\subcaptionbox{Weighted prior}{\includegraphics[width=0.19\columnwidth, height=0.2\textheight]{../images/thesis/okra/zoomed/weighted_prior_cropped.png}}
\caption[Zoomed results of Okra dataset]{Zoomed RoI of Fig.~\ref{fig:okra_3D_results} (b) strong streak artefacts, %(c) blurred,
  (c) no new  information detected (prior dominates -- the deformity from the prior
  shows up as a false positive) and (d) new information detected (no deformities).}
\label{fig:okra_zoomed_3D_results}
\end{figure}

@@

\vspace{0.5cm}\textcolor{blue}{\textbf{[R2-3]:} \textit{In several parts of the
    paper, the authors claim that existing object-prior based methods
    have problems, e.g.: "A common problem with these techniques is
    the strong influence of object-priors in the reconstruction of new
    regions in the test". At the moment, this hard claim is not
    supported in the paper by references or (even better) comparison
    results. It would be good to show, on one (or more) of the
    datasets used, that this is indeed the case, and that the proposed
    methods solves this problem.}}

\textbf{Response:} We have now included a reference (Pg.2, Line 3
under Sec.1-A) to a PhD thesis wherein the problem of object-priors
biasing the reconstruction of new test regions is discussed in detail.
A sample result (Figures 1-3) from the thesis is shown. It
illustrates how an unweighted application of prior (equivalent to $\boldsymbol{W}$ being Identity matrix in Eq.3 of our paper) can adversely
affect the reconstruction of new regions in the test.

### 2022-02-16 paper/post_tci.tex
minor edits
Rewritten DL-Lit in paper and reponse sheet

 In the recent past, deep learning based techniques have also been widely used for limited view CT reconstruction without the use of any longitudinal object-prior. For example, in~\cite{anirudh}, a neural network is trained to predict the complete sinogram from an incomplete one obtained from few-view imaging. This complete sinogram is then fed to analytical reconstruction algorithms to obtain the final reconstruction. Hence, one may in principle use this full sinogram as an alternate initial reconstruction of the test within our framework. \cite{bo2021} presented a cascade of neural networks that predict full-view reconstruction from limited view FBP reconstruction while simlutaneously ensuring consistency between the predicted sinugram and the acquired sinogram. \cite{special} trains an adverserial network for artifact removal and edge preservation in limited view reconstruction. While all of the above methods predict full-view reconstruction from the measurements of test object alone, we believe it is beneficial to use information from longitudinal data, especially if naturally available, like in the radio-frequency ablation datasets that we use. In this context, we present an analytical method that uses the available longitudinal data to better inform the reconstruction of the test. We first construct a `weights map' that gives clear insights about regions of change within the object over time.

>>>>

In the recent past, deep learning based techniques~\cite{anirudh},\cite{kim2019extreme},\cite{bo2021},\cite{special} have also been widely used for limited view CT reconstruction. For example, in~\cite{anirudh}, a neural network is trained to predict the complete sinogram from an incomplete one.% This complete sinogram is then fed to analytical reconstruction algorithms to obtain the final reconstruction.
 ~\cite{bo2021} presented a cascade of neural networks that predict full-view reconstruction from limited view FBP reconstruction while simlutaneously ensuring consistency between the predicted sinugram and the acquired sinogram. \cite{special} trains an adverserial network for artifact removal and edge preservation in limited view reconstruction. In this work, the ability of these techniques to
uncover new features from one or many example training images is not being disputed. Instead, we focus is on a new discrete algorithm that builds structural maps that can and does point to new features. Having said that, our work is complementary to learning-based teachniques and can fit alongside a deep learning framework. For example, in~\cite{kim2019extreme}, an adversarial network is used to predict a reconstruction from extremely sparse measurements. This is used as an initialization in  a traditional iterative reconstruction algorithm to compute the final reconstruction. Given this pipeline, our method can be used to further inform the iterative algorithm of the available template information, as presented in Fig.~\ref{fig:Lit}.

    %Hence, one may in principle use this full sinogram as an alternate initial reconstruction of the test within our framework.
      We further note that all of the above existing methods predict full-view reconstruction from the measurements of test object alone. We believe it is beneficial to use information from longitudinal data, especially if naturally available, like in the radio-frequency ablation datasets that we use. In this context, we present an analytical method that uses the available longitudinal data to better inform the reconstruction of the test. We first construct a `weights map' that gives clear insights about regions of change within the object over time.

\begin{figure}[t]
\centering
	\includegraphics[width=0.5\textwidth]{../images/Lit.png}
        \caption{Illustration of the application of our method (marked in yellow, red) within the deep learning based framework presented in~\cite{kim2019extreme}.}
 \label{fig:Lit}
 \end{figure}
